---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# moodleQuiz

<!-- badges: start -->

<!-- badges: end -->

The goal of the `moodleQuiz` package is to perform data wrangling, merging and analyse [Moodle Quiz report](https://docs.moodle.org/311/en/Quiz_reports) with simple ready-to-use functions.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Lightbridge-AI/moodleQuiz")
```

## Combine Student Grades

This is an example of Moodle Grades report:

```{r grades_rep ex}
library(moodleQuiz)
data("grades_ls")

head(grades_ls$Quiz_1)
```

Suppose that you have multiple reports, you can combine them in to a list of data frame

```{r grades_ls}
# the example data "grades_ls" is a named list of data frame.
class(grades_ls)
purrr::map(grades_ls, class)
```

Then, you can combine multiple Grades report to a single data frame with: `combine_grades()`

```{r example}
combine_grades(grades_ls)
```
