---
title: "moodleQuiz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{moodleQuiz}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

[Moodle](https://moodle.org), a learning management system, store data related to *quiz taking* in [Moodle Quiz Report](https://docs.moodle.org/311/en/Quiz_reports) which has 4 types: Grades report, Responses report, Statistic report, and Manual grading.

`{moodleQuiz}` package have a functions that operate specifically on 2 types of report: **Grades report** and **Responses report**. The notable difference between the 2 are:

-   **Grades report** has columns started with `Q. x /x`, these columns store score of each questions.

-   **Responses report** has columns started with `Response x`, these columns store raw text responses of each questions.

The rest of the columns are the same for these 2 reports:

-   `Surname`: student's last name, `First name`: student's first name

-   `Institution`: student's institution, `Department`: student's department

-   `Email address`: student's Email (often, an educational account)

-   `State`: the state of the attempt usually have 2 values, one of: **"Finished"** for submitted attempt, and **"In progress"** for ongoing not-yet-submitted attempt.

-   `Started on` and `Completed` are the time point at which student started and submitted the quiz. `Time taken` is a duration from started to submitted the quiz.

-   `Grade/xx`: total student's score (if present) of the quiz.

## Getting Data

**Grades report** and **Responses report** can be downloaded from Moodle server in various formats (e.g., `.csv`, `.xlsx`, `.json`). You have to find a way to import that report in to `R` as **a data frame or list of data frames**, which is the data structure in which functions in `{moodleQuiz}` package will operate on.

Once you imported the report into `R`, do not format or clean anything prior to passing into the functions that I will introduce to you next.

## Example Data

`{moodleQuiz}` package comes with example data of Grade reports and Responses reports.

```{r setup, message=FALSE, warning=FALSE}
library(moodleQuiz)
library(dplyr)
```

### Grades Reports

`grades_ls` is a *list* containing `r length(grades_ls)` *data frames* of **Moodle Grades Report**.

```{r}
class(grades_ls)
```

Each elements are data frames of Grade reports from `r length(grades_ls)` *different quiz* that the *same* group of students have completed.

```{r}
names(grades_ls)
```

For example, this is the Grade report of `Quiz_1`

```{r}
head(grades_ls$Quiz_1)
```

Notice the last row here which is an "Overall average" that Moodle calculated for us.

```{r}
grades_ls$Quiz_1 %>% 
  select(Surname, starts_with("G"), starts_with("Q")) %>% 
  tail(1)
```

### Responses Report

`responses_ls` is a *list* containing `r length(responses_ls)` *data frames* of **Moodle Responses Report**. Each data frame is a quiz that the *same* group of students have done.

```{r}
names(responses_ls)
```

```{r}
head(responses_ls$Quiz_1)
```

## Check Submission

`check_sub()` check student submission from `state` column of Grades or Responses report.

Calling this function would

1.  Clean and format column names

2.  Encode `State` column resulting in `Encode` column, "Finished" attempt encoded as 1, and "In progress" attempt encoded as 0.

3.  Filter rows by time and encoding. By default, It choose the first maximum score of each student.


**Check Submission of Quiz 1**


```{r}
grades_ls$Quiz_1 %>%
  check_sub(id_regex = "[:digit:]+") %>%
  select(Name, ID, State, Encode)
```

**Check Submission of All Quizzes**


You can check whether student submit multiple quizzes by passing **a list of data frames** as show here as `grades_ls`.


```{r}
grades_ls %>%
  check_sub(id_regex = "[:digit:]+") %>%
  select(Name, ID, ends_with("Encode"), Total)
```

Notice that the name of each data frame (e.g., "Quiz_1") are prefix in the column names, and `Total` column is calculated by sum of encoding by each student in each quiz. 

Now you can check whether students submit each quizzes in a course and how many they missed by just calling one function!


## Combine Responses



`combine_resp()` combine student's responses (`Response x`) from the **Responses report**.


Calling this function would

1.  Clean and format column names

2.  Filter rows by time and encoding. By default, It choose the first maximum score of each student.

3.  Return data frame with `Response_x` columns


**Combine Response of Quiz 1**

This would get similar result to `check_sub()`, except it also return `Response_*` column and has an ability to split **Cloze columns**.

```{r}
responses_ls$Quiz_1 %>%
  combine_resp(id_regex = "[:digit:]+") %>%
  select(Name, ID, starts_with("R"))
```

**Combine Response of All Quizzes**


Calling `combine_resp()` on a *list of data frame* would get all responses of each students combined in 1 data frame.


```{r}
responses_ls %>%
  combine_resp(id_regex = "[:digit:]+") %>%
  select(Name, ID, contains("R")) %>%
  glimpse()
```

Notice that the name of each data frame (e.g., "Quiz_1") are prefix in the column names.

## Count Responses

`count_resp()` counts how many responses each student answered from the **Responses report**.

Calling this function would

1.  Clean and format column names

2.  Filter rows by time and encoding. By default, It choose the first maximum score of each student.

3.  Return data frame with `Count_Resp_x` columns


In contrast to `combine_resp()`, `count_resp()` returns **counts** of how many responses do each students answered.

Beware that `count_resp()` counts any non-blank answers that is not `-` (dash) as an answers, even though it is not appropriate to the question.  


**Count Responses of Quiz 1**


```{r}
responses_ls$Quiz_1 %>%
  count_resp(id_regex = "[:digit:]+") %>%
  select(Name, ID, starts_with("Count"))
```


**Count Responses from All Quizzes**

Calling `count_resp()` on a *list of data frame* would yields counts of responses for all quizzes and the total counts is calculated.

```{r}
responses_ls %>%
  count_resp(id_regex = "[:digit:]+") %>%
  select(Name, ID, contains("Count"), starts_with("Total"))
```

Using `count_resp()` to checking response counts can be a great way to check whether student did the quiz as expected, since the checking is done **per questions**, while `check_sub()` only check for **student's submission** of the quiz. 

Interestingly, If the student did every questions from the quiz and forgot to press the "Submit all and finished" button, the result from `check_sub()` would shows that student didn't do the quiz ("In progress"), while `count_resp()` can reveal that student do the quiz with that many questions answered.


## Combine Grades


`combine_grades()` filter, adjust, and combine student's grade from `Grade/xx` column.


Calling this function would

1.  Clean and format column names

2.  Filter rows by time and grade. By default, It choose the first maximum score of each student.

3.  Return data frame with `Grade_x` columns (and may be `Qx`)


**Combine & Adjust Grades of Quiz 1**

You can filter grade by `choose_grade` parameter and readjust maximum grade to any score by `new_max_grade` parameter.


```{r}
grades_ls$Quiz_1 %>%
  combine_grades(
    id_regex = "[:digit:]+",
    choose_grade = "max", # Choose only maximum grade of each student
    new_max_grade = 100 # Adjust maximum grade to 100
  ) %>%
  select(Name, ID, starts_with("G"), starts_with("Q"))
```


**Combine Grades for All Quizzes**

Calling `combine_grades()` on *list of data frame* would combine the score of each quizzes from each student in to 1 data frame, and `Total_x` column will be added as a sum of student's score.

You can adjust the maximum score of each individual quizzes by input `new_max_grade` as a numeric vector corresponding to each quiz. In this example, I will adjust the maximum score of "Quiz_1" and "Quiz_2" to 25, and "Quiz_3" to 50.


```{r}
grades_ls %>%
  combine_grades(
    id_regex = "[:digit:]+",
    choose_grade = "max", # Choose only maximum grade of each student
    new_max_grade = c(25, 25, 50) # Maximum score of each quizzes
  ) %>%
  select(Name, ID, contains("Grade"), starts_with("Total")) %>%
  glimpse()
```


---

Last updated: `r Sys.Date()`

